### 2013-05-13 inst/examples/BUGS/policy_thresholds.Rmd
Adjusted penalty for policy thresholds case
* Need to make sure each algorithm permits the flexible choise of policy function
* Compare severe penalty case to zero-profit case

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA,
               fig.width=6, fig.height=4)

library(knitcitations)

@@

```{r}
f <- Ricker
p <- c(2, 8)
K <- p[2]
C <- 5 # policy threshold
```

@@

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h) * (x > C) # no money for violating threshold
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <- K # observations start from
x0 <- Xo # simulation under policy starts from
Tobs <- 40
```

@@

```{r obs, dependson="sdp-pars"}
  set.seed(1234)
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- 6
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
```

@@

```{r mle, dependson="obs"}
alt <- par_est(obs,  init = c(r = p[1], 
                              K = mean(obs$x[obs$x>0]), 
                              s = sigma_g))
est <- par_est_allee(obs, f, p,  
                     init = c(r = p[1] + 1, 
                              K = p[2] + 2, 
                              C = p[3] + 2, 
                              s = sigma_g))
```

@@

```{r}
jags.data <- list("N","y")
n.chains = 1
n.iter = 400000
n.burnin = floor(10000)
n.thin = max(1, floor(n.chains * (n.iter - n.burnin)/1000))
```

@@

### Parametric Bayes based on myers model

Contains the

init_p = c(1, 1, 1)
names(init_p) = c("r0", "theta", "K")
y <- obs$x[-1] 
N=length(y);
```

```{r}
jags.params=c("logr0", "logtheta", "logK", "stdQ", "stdR")
jags.inits <- function(){
  list("logr0"=log(init_p["r0"]), "logtheta" = log(init_p["theta"]),  
       "logK"=log(init_p["K"]), "stdQ"=sqrt(0.05), 
       "stdR"=sqrt(0.1),"x"=y,.RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
```

```{r}
set.seed(12345)
time_jags <- system.time(       
  jagsfit <- jags(data=jags.data, inits=jags.inits, jags.params, 
                  n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                  n.burnin=n.burnin, model.file="myers.bugs")
)         
time_jags <- unname(time_jags["elapsed"]);
```

Convergence diagnostics for parametric bayes

```{r}
jags_matrix <- as.data.frame(as.mcmc.bugs(jagsfit$BUGSoutput))
par_posteriors <- melt(cbind(index = 1:dim(jags_matrix)[1], jags_matrix), id = "index")

## Traces
ggplot(par_posteriors) + geom_line(aes(index, value)) +
  facet_wrap(~ variable, scale="free", ncol=1)

```{r}
## prior curve functions, must be in order
par_priors <- list( deviance = function(x) 0 * x, logK = logK_prior,
                    logr0 = logr_prior, logtheta = logtheta_prior, 
                    stdQ = stdQ_prior, stdR = stdR_prior)

## calculate points along the prior curve
par_prior_curves <- ddply(par_posteriors, "variable", function(dd){
    grid <- seq(min(dd$value), max(dd$value), length = 100) 
    data.frame(value = grid, density = par_priors[[dd$variable[1]]](grid))
})
```

```{r}
## posterior distributions
ggplot(par_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  geom_line(data=par_prior_curves, aes(x=value, y=density), col="red") + 
  facet_wrap(~ variable, scale="free", ncol=2)
```

```{r}
myers_pardist <- as.matrix(jags_matrix[2:6])
myers_pardist[,1] = exp(myers_pardist[,1]) # transform model parameters back first
myers_pardist[,2] = exp(myers_pardist[,2]) # transform model parameters back first
myers_pardist[,3] = exp(myers_pardist[,3]) # transform model parameters back first
colnames(myers_pardist) = c("K", "r0", "theta", "stdQ", "stdR")

apply(myers_pardist,2,mean)
bayes_coef <- apply(myers_pardist,2, posterior.mode) # much better estimates

myers_bayes_pars <- unname(c(bayes_coef[2], bayes_coef[3], bayes_coef[1]))
```

@@

```{r}
true_means <- sapply(x_grid, f, 0, p)
alt_means <- sapply(x_grid, alt$f, 0, ricker_bayes_pars[c(1,2)])
est_means <- sapply(x_grid, est$f, 0, est$p)
par_bayes_means <- sapply(x_grid, f, 0, bayes_pars)

myers_means <- sapply(x_grid, Myer_harvest, 0, myers_bayes_pars)

models <- data.frame(x=x_grid, GP=tgp_dat$y, True=true_means, 
                     MLE=est_means, Ricker=alt_means, 
                     Parametric.Bayes = par_bayes_means,
                     Myers = myers_means)

@@

```{r}
ricker_f <- function(x, h, p) alt$f(x, h, unname(p[c(2, 1)]))
matrices_alt <- parameter_uncertainty_SDP(ricker_f, x_grid, h_grid, as.matrix(ricker_pardist), 3)
opt_alt <- value_iteration(matrices_alt, x_grid, h_grid, OptTime=MaxT, xT, profit, delta=delta)
```

Bayesian Myers model

```{r}
myers_f <- function(x,h,p) Myer_harvest(x, h, p[c(2, 3, 1)])
matrices_myers <- parameter_uncertainty_SDP(myers_f, x_grid, h_grid, as.matrix(myers_pardist), 4)
myers_alt <- value_iteration(matrices_myers, x_grid, h_grid, OptTime=MaxT, xT, profit, delta=delta)
```

@@

```{r}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_alt$D, Parametric.Bayes = opt_par_bayes$D, Myers = myers_alt$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```

>>>>

```{r plotting-options}
library(knitcitations)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA,
               fig.width=6, fig.height=4)

@@

```{r}
f <- Ricker
p <- c(.5, 10)
K <- p[2]
C <- 5 # policy threshold
```

@@

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h) - 10*(x > C) # big penalty for violating threshold
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <- K # observations start from
x0 <- Xo # simulation under policy starts from
Tobs <- 40
```

@@

```{r obs, dependson="sdp-pars"}
  set.seed(1234)
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- 6
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
# plot(x)
```

@@

```{r mle, dependson="obs"}
est <- par_est(obs,  init = c(r = p[1], 
                              K = mean(obs$x[obs$x>0]), 
                              s = sigma_g))

@@

@@

@@

```{r}
true_means <- sapply(x_grid, f, 0, p)
mle_means <- sapply(x_grid, est$f, 0, est$p)
ricker_means <- sapply(x_grid, est$f, 0, ricker_bayes_pars[c(1,2)])
allen_means <- sapply(x_grid, f, 0, bayes_pars)

# myers_means <- sapply(x_grid, Myer_harvest, 0, myers_bayes_pars)

models <- data.frame(x=x_grid, GP=tgp_dat$y, True=true_means, 
                     MLE=mle_means, Ricker = ricker_means,
                     Allen = allen_means)

@@

```{r}
ricker_f <- function(x, h, p) est$f(x, h, unname(p[c(2, 1)]))
matrices_alt <- parameter_uncertainty_SDP(ricker_f, x_grid, h_grid, as.matrix(ricker_pardist), 3)
opt_alt <- value_iteration(matrices_alt, x_grid, h_grid, OptTime=MaxT, xT, profit, delta=delta)
```

@@

```{r}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_alt$D, Allen = opt_par_bayes$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```
